**Preprinting Microbiology**

### 2017-02-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Incorporate Stefano's edits

The field of microbiology has experience significant growth due to rapid advances in technology and the influx of scientists driven by a curiosity to understand how bacteria, archaea, microbial eukaryotes, and viruses interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth. With this explosion in scientific output, a significant bottleneck has been the ability to disseminate this new knowledge to peers and the public in a timely manner. Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit a broader pool of reviewers prior to submitting to traditional journals. Although use of preprints is still limited in the biological sciences, early indications are that preprints are as robust and impactful as peer-reviewed papers. As publishing moves to embrace advances in internet technology, there are many opportunities for scientists and publishers to benefit from the use of preprints.

@@

***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public. A preprint is an unpublished manuscript that is made publicly available without going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016]. An author can post their manuscript to a preprint server for others to read, share, and make comments. Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966]. While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011]. Among physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become the standard publication strategy. Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists. Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012]. Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses of and concerns regarding preprints.

***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013]. Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in under 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded. There are several important differences between the two options. First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory. This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations. Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse. This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. *Proceedings of the National Academy of Sciences*). A cosmetic, but still relevant difference between the two is the layout and feel of the two websites. Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints. With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*. It is only possible to transfer a *PeerJ Preprint* for submission to *PeerJ*. In many ways, preprint servers have taken on the feel of a journal. As adoption of this approach expands, it is likely that the features of these sites will continue to improve. It is also likely that interfaces from third-parties will improve. For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not. There is also hope that the National Institutes of Health (NIH) will renew their interest in including preprints in PubMed search results. As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, it will be important to balance the requirements placed on authors for those features with the current efficiency of the preprint format.

***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider. It is critical that assurances be given that policies are in place to address these issues. First, a significant amount of attention has been given to the potential dual use of microbiology research for individuals seeking to engage in terrorist activities. Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research. Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results. Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism. Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.

***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication. The broad consensus at this point is that preprints do not constitute prior publication. This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, and *Nature*, which have a permissive stance towards prior posting of preprints prior to submission. Although journals published by Cell Press do not forbid authors from posting preprints prior to submission, they ask authors to consult an editor prior to posting and do not allow authors to post revised preprints that contain revisions that respond to editorial input. Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work. Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].

@@

***Preprints have the potential to change the advancement of science.*** Preprints are often viewed as existing in a state of scientific limbo. As noted above, they represent a formal communication, but are not officially published. As the use of preprints grows and scientists' perceptions of preprints matures, there are a number of issues that will need to be addressed.

First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the preprint author will lose their ability to claim primacy or their ability to publish the work in a journal. Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second. A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016]. Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016]. This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.

A second area of concern is whether a preprint can be used to support a grant proposal. Given the length limitations placed on grant proposals by funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data. Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts. We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science.

@@

Beyond these concerns, preprints are also causing some to change their publication goals. Some authors are explicitly stating that a preprint will not be submitted to a journal [@SinghChawla2017]. Although these authors may be a minority of those who post preprints, such an approach may be attractive to those that want to have a mechanism for people to cite a report of a brief research communication, a critique of another publication, or negative results. It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work. There is great potential to empower researchers by controlling when a citable piece of work is made public.

@@

Second, preprints have proven useful for rapidly correcting the scientific literature. On February 9, 2015, *Cell Systems* posted a study by Afshinnekoo et al. online [@Afshinnekoo2015a]. The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*. Because of the focus on these two bioterrorism agents, this study generated a considerable amount of media attention. On April 25, 2015, Petit et al. [@Petit2015] posted a preprint to Zenodo demonstrating that there was no evidence for *B. anthracis* in the dataset. On July 29, 2015, a critique was published by *Cell Systems* along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b]. A second anecdote of using preprints to aid in post-publication peer-review surrounds the publishing of a draft tardigrade genome in *The Proceedings of the National Academy of Sciences*. On November 23, 2015 a study by Boothby et al. [@Boothby2015] was first published online. The authors posited that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses. Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result. A week later, on December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b]. Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016]. These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases. A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al. reporting numerous cases of image manipulation in peer reviewed studies [@Bik2016a]. Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016 [@Bik2016b]. Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.

@@

As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process. Among the microbiology-affiliated preprints, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature. Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback. Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once. Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published. As noted above, not all authors submit their preprints to journals. This would indicate that the "acceptance rates" are actually higher. Regardless, considering that these acceptance rates are higher than many peer-reviewed journals (e.g. approximately 20% at ASM Journals), these results dispel the critique that preprints represent overly preliminary research.

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics we sought to quantify the effect that microbiology-affiliated preprints have had on the work of others. Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**). The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric]. A higher score indicates that a preprint received more attention. Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *biorxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`. A more traditional and controversial metric of impact has been the number of citations an article receives. We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, we considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**). Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`). For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`). Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community

@@

***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints. One perspective is that although authors value immediate accessibility to their work, they also value the editorial support from professional societies and other organizations. Furthermore, the professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to address what they can offer preprint authors. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. A new venture from *mSphere*, mSphereDirect, actively encourages authors to post their manuscripts as preprints as part of the author-driven editorial process [@Imperiale2016]. In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.

>>>>

The field of microbiology has experienced significant growth due to transformative advances in technology and the influx of scientists driven by a curiosity to understand how bacteria, archaea, microbial eukaryotes, and viruses interact with each other and their environment to sustain myriad biochemical processes that are essential for maintaining the Earth. With this explosion in scientific output, a significant bottleneck has been the ability to disseminate this new knowledge to peers and the public in a timely manner. Preprints have emerged as a tool that a growing number of microbiologists are using to overcome this bottleneck and to recruit in an effective and transparent way a broader pool of reviewers prior to submitting to traditional journals. Although use of preprints is still limited in the biological sciences, early indications are that preprints are as robust tool that can complement and enhance peer-reviewed publications. As publishing moves to embrace advances in internet technology, there are many opportunities for preprints and peer-reviewed journals to coexist in the same ecosystem.

@@

***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public. A preprint is an interim research product, such as an unpublished manuscript, made publicly available before going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016]. Authors can post their manuscript to a preprint server for others to read, share, and comment. Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966]. While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011]. For some physicists and mathematicians, posting a preprint to *arXiv* followed by submission to a peer-reviewed journal has become a standard publication pathway. Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists. Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012]. Considering the broadening adoption of preprints among microbiologists, we sought to explore the specific uses of and concerns regarding preprints.

***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013]. Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded. There are several important differences between the two options. First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory. This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations. Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse. This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. *Proceedings of the National Academy of Sciences*). We particularly like the *bioRxiv* licensing flexibility, which empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research resultsl however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option. A cosmetic, but still relevant difference between the two is the layout and feel of the two websites. Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints. With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*. It is only possible to transfer a *PeerJ Preprint* for submission to *PeerJ*. In many ways, preprint servers have taken on the feel of a journal. As adoption of this approach expands, it is likely that the features of these sites will continue to improve. It is also likely that interfaces from third-parties will improve. For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not. There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications. As preprint servers begin to look and act like traditional journals by incorporating features and interfaces, we think that it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted. It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.

***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider. It is critical that assurances be given that policies are in place to address these issues. First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities. Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research. Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results. Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism or misconduct. Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers.

***Acceptance of preprints by journals.*** An early controversy encountered by researchers interested in posting their work as preprints as a stage in disseminating their research was whether it constituted prior publication. The broad consensus at this point is that preprints do not constitute prior publication. This consensus is reflected in the current policies of journals that commonly publish microbiology research including those published by ASM, the Microbiology Society, International Society for Microbial Ecology, PLOS, the *Proceedings of the National Academy of Science*, *Science*, *Nature* and Cell press, which each take a generally permissive stance towards prior posting of preprints prior to submission. Considering the relatively fluid nature of many of these policies and the journals' specific policies, prospective authors should be aware of the positions taken by the journals where they may eventually submit their work. Comprehensive lists of journals' attitudes towards preprints are available online and are regularly updated [@PreprintPolicy; @Sherpa].

@@

***Preprints have the potential to change the advancement of science.*** Preprints are often viewed as existing in a state of scientific limbo. As noted above, they represent a formal communication, but an interim one, not officially published. As the use of preprints grows and scientists' perceptions of preprints matures, there are a number of issues that will need to be addressed.

First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the preprint author will lose their ability to claim primacy or their ability to publish the work in a journal. Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second. The use of preprints uncouples the communication of the discovery from the relevance of the discovery, which will come later based on peer-review, comments from other scientists at meetings or online, and eventually citations. A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016]. Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016]. This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data.

A second area of concern is whether a preprint can be used to support a grant proposal. Given the length limitations placed on grant proposals by funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data. Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts. We would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science. This would be greatly facilitated if funding agencies would include preprints as evidence for research progress, but listed separately from peer-reviewed publications to help review panels in their decisions and to help author substantiate evidence they feel they need to provide.

@@

Beyond these concerns, preprints are also causing some to change their publication goals. Some authors are explicitly stating that a preprint will not be submitted to a journal [@SinghChawla2017]. Although these authors may be a minority of those who post preprints, such an approach may be attractive to those who need to cite a report of a brief research communication, a critique of another publication, or negative results. It is clear that the adoption of preprints will challenge how scientists interact and evaluate each other's work. There is great potential to empower researchers by controlling when a citable piece of work is made public.

@@

Second, preprints have proven useful for rapidly correcting the scientific literature. On February 9, 2015, *Cell Systems* posted a study by Afshinnekoo et al. online [@Afshinnekoo2015a]. The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*. Because of the focus on these two bioterrorism agents, this study generated a considerable amount of media attention. On April 25, 2015, Petit et al. [@Petit2015] posted a preprint to Zenodo demonstrating that there was no evidence for *B. anthracis* in the dataset. On July 29, 2015, a critique was published by *Cell Systems* along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b]. A second anecdote of using preprints to aid in post-publication peer-review surrounds the publishing of a draft tardigrade genome in *The Proceedings of the National Academy of Sciences*. On November 23, 2015 a study by Boothby et al. [@Boothby2015] was first published online. The authors claimed that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses. Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result. A week later, on December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b]. Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016]. These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases. A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al. reporting numerous cases of image manipulation in peer reviewed studies [@Bik2016a]. Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016 [@Bik2016b]. Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.

@@

As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process. Among the microbiology-affiliated preprints, `r n_micro_aff_ever_commented` (`r 100*n_micro_aff_ever_commented/sum(micro_affiliated, na.rm=T)`%) had been commented on at least once and only `r n_micro_aff_thrice_commented` (`r 100*n_micro_aff_thrice_commented/sum(micro_affiliated, na.rm=T)`%) more than three times using the *bioRxiv*-hosted commenting feature. Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback. We understand that it is not in the tradition of the scientific community to comment publicly online about colleagues’ research results.  We think this will change given the possibilities of new media, and possibly incentives for open commenting and reviewing could shift the trend. Importantly, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as `r n_micro_aff_revised` (`r 100*n_micro_aff_revised/sum(micro_affiliated, na.rm=T)`%) of preprints were revised at least once. Among the preprints posted prior to January 1, 2016, `r 100*n_micro_published/sum(biorxiv$category == "Microbiology", na.rm=T)`% of the Microbiology category preprints, `r 100*n_micro_aff_published/sum(micro_affiliated, na.rm=T)`% of the microbiology-affiliated preprints, and `r 100*n_all_published/nrow(biorxiv)`% of all preprints have been published. As noted above, not all authors submit their preprints to journals. This would indicate that the "acceptance rates" are actually higher. Regardless, considering that these acceptance rates are higher than many peer-reviewed journals (e.g. approximately 20% at ASM Journals), these results dispel the critique that preprints represent overly preliminary research.

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics we sought to quantify the effect that broadly defined microbiology-affiliated preprints have had on the work of others. Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was `r median(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'abstract_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`) and `r median(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T)` (IQR: `r paste(quantile(biorxiv[micro_affiliated, 'pdf_downloads'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint (**Figure 1B**). The Altmetric Attention Score measures the number of times a preprint or paper is mentioned in social media, traditional media, Wikipedia, policy documents, and other sources [@Altmetric]. A higher score indicates that a preprint received more attention. Microbiology-affiliated preprints have had a median Altmetric Attention Score of `r median(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[micro_affiliated, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`) and those of all preprints hosted at *bioRxiv* have had a median score of `r median(biorxiv[, 'altmetric_score'], na.rm=T)` (IQR: `r paste(round(quantile(biorxiv[, 'altmetric_score'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). For comparison, the median Altmetric Attention Score for articles published in *mBio* published since 2013 was `r median(mbio[, 'altmetric'], na.rm=T)` (IQR: `r paste(round(quantile(mbio[, 'altmetric'], na.rm=T, probs=c(0.25, 0.75)), 1), collapse=' to ')`). Of all scholarship tracked by Altmetric, the median Altmetric Attention Score for preprints posted at *bioRxiv* ranks at the `r median(biorxiv[, 'altmetric_percentile'], na.rm=T)` percentile (IQR: `r paste(quantile(biorxiv[, 'altmetric_percentile'], na.rm=T, probs=c(0.25, 0.75)), collapse=' to ')`. A more traditional and controversial metric of impact has been the number of citations an article receives. We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, we considered the citations for preprints published in 2014 and 2015 as aggregated by Web of Science (**Figure 1C**). Among the preprints that were published and could be found in the Web of Science database, the median number of citations was `r median(biorxiv_cited_affiliated_2015)` (IQR: `r paste(quantile(biorxiv_cited_affiliated_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(biorxiv_cited_affiliated_2015)`). For comparison, for the papers published in *mBio* in 2014 and 2015, the median number of citations was `r median(mbio_cited_2015)` (IQR: `r paste(quantile(mbio_cited_2015, prob=c(0.25,0.75)), collapse='-')`; mean: `r mean(mbio_cited_2015)`). Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community.

@@

***Preprints from a publisher's perspective.*** A lingering question is what role traditional journals will have in disseminating research if there is broad adoption of preprints. We think that edited peer-reviewed journals offer, and will continue to offer significant added value to a publication. A scholarly publishing ecosystem in which preprints coexist with journals will allow authors to gain value from the immediate communication of their work associated with preprints and also benefit from the peer-reviewed, professionally edited publication that publishers can provide.
The professional copyediting, layout, and publicity that these publishers offer are also unique features of traditional journals. An alternative perspective is that preprints will eventually replace traditional journals. Certainly, this is a radical perspective, but it does serve to motivate publishers to capture the innovation opportunities offered by preprints. By adopting preprint-friendly policies, journals can create an attractive environment for authors. As discussed above, a growing number of journals have created mechanisms for authors to directly submit preprints to their journals. An example is offered by the ASM, which earlier this year launched a new venture from *mSphere*. mSphereDirect is a publication track of the journal that capitalizes on the opportunity offered to couple preprints with rigorous peer-review. mSphereDirect. actively encourages authors to post their manuscripts as preprints as part of an author-driven editorial process where an editorial decision is rendered within five days and publication in *mSphere* within a month [@Imperiale2016]. ASM is developing a new platform, MicroNow, which will help coalesce specific communities within the microbial sciences, further enhancing the use of preprints as well as published articles. In addition to integrating preprints into the traditional editorial process, several professional societies have also explicitly supported citation of preprints in their other publications and recognize the priority of preprints in the literature [@Pulverer2016; @Loew2016; @Vale2016]. These are policies that empower authors and make specific journals more attractive. Other practices have great potential to improve the reputation of journals. As measured above, preprints are able to garner attention on par with papers published in highly selective microbiology journals. Thus, it is in a journal's best interest to recruit these preprints to their journals. Several journals including *PLOS Genetics* and *Genome Biology* have publicly stated that they scout preprints for this purpose [@Vence2017; @Barsh2016]. Preprints can also be viewed as a lost opportunity to journals. A preprint that garners significant attention may be ignored when it is finally published, brining little additional attention to the journal. Going forward, it will be interesting to see the innovative approaches that publishers develop so that they can benefit by incorporating preprints into their process and whether publishers' influence is reduced by the widespread adoption of preprints.
